### 2023-03-24 resilience.tex
Up
details

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^k(\Safe)= \uparrow~\pred^k(\Safe)$ for all $k \in \N$,
and there exists $K \in \N$ such that 
$\pred^k(\Safe) = \uparrow \pred^k(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
Hence the equivalence.
\end{proof}

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^k(\Safe)= \uparrow~\pred^k(\Safe)$ for all $k \in \N$, and $\pred^k(\Safe)$ admits a finite basis $B_{\pred^k(\Safe)}$. From a similar reasoning as above, the $k$-resilience problem is decidable.
\end{proof}

@@

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$.
The resilience problem (RP) and the bounded resilience problem (BRP) are decidable.
\end{theorem}

@@

To decide the  bounded resilience problem (BRP), we decide $n \times m$ coverability questions: is state $b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_a \mid a=1,..,m \times n)$ and we deduce that  $\mathscr{S}$ is   $K$-resilient. Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we have shown that both the 
  resilience problem (BRP) and the  
  bounded resilience problem (BRP) are decidable.
\end{proof}

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$.
The  $k$-resilience problem (kRP) is decidable. \textcolor{red}{CONJECTURE for now}
 \end{theorem}

>>>>

\iffalse

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^n(\Safe)= \uparrow~\pred^n(\Safe)$ for all $n \in \N$,
and there exists $k \in \N$ \alain{K pas utilisé} such that 
$\pred^k(\Safe) = \uparrow \pred^k(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
Hence the equivalence.
\end{proof}

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^k(\Safe)= \uparrow~\pred^k(\Safe)$ for all $k \in \N$, and $\pred^k(\Safe)$ admits a finite basis $B_{\pred^k(\Safe)}$. From a similar reasoning as above, the $k$-resilience problem is decidable.\alain{réserver k pour le k-résilience, il y a d'autres lettres...n, m, p,...}
\end{proof}

@@

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$ \alain{Min ou B ?}.
The resilience problem (RP) and the bounded resilience problem (BRP) are decidable.
\end{theorem}

@@

To decide the  bounded resilience problem (BRP), we decide $n \times m$ coverability questions: is state $b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_a \mid a=1,..,m \times n)$ and we deduce that  $\mathscr{S}$ is $K$-resilient \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ?}. Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we have shown that both the 
  resilience problem (BRP) and the  
  bounded resilience problem (BRP) are decidable.
\end{proof}

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$.
The  $k$-resilience problem (kRP) is decidable for $k \geq K$. \textcolor{red}{CONJECTURE for now}
 \end{theorem}
